### 2011-12-14 doc/theses/mikula/used_technologies_and_definitions.tex
Master thesis: In progress.

Various languages have been proposed to express XML schemata. The most known are Document Type Definition (DTD) \todo{link} and XML Schema Definition (XML Schema, XSD) \todo{link} which are briefly described in the following sections. Another examples of the XML schema languages are RELAX NG \todo{link} and  Schematron \todo{link}.

A validity of an XML document againt its XML schema expresses wheather the document is well-formed \todo{link}, and at the same time, wheather it conforms to the XML schema.

>>>>

Various languages have been proposed to express XML schemata. The most known are Document Type Definition (DTD) \cite{Bray:08:EML} and XML Schema Definition (XML Schema, XSD) \cite{Walmsley:04:XSP, Thompson:04:XSP, Malhotra:04:XSP} which are briefly described in the following sections. Another examples of the XML schema languages are RELAX NG \cite{relaxng} and  Schematron \cite{schematron}.

A validity of an XML document againt its XML schema expresses wheather the document is well-formed \cite{Bray:08:EML}, and at the same time, wheather it conforms to the XML schema.
